---
title: "learnR report 2017"
author: "Mark Kelson"
date: "16 June 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Following a scoping visit conducted by Mark Kelson (MK) over June 2016, a priority objective was identified to deliver training in statistical software. The choice of software is the free, open-source, enterprise-ready software R. Over the course of the following 12 months MK organized a team of statistical and R experts to develop a three day introductory training course in R. Monthly skype contacts with our lead local organiser Lilian Pazvakawambwa (LP) were maintained over this period. In addition Dave Gillespie (DG) and Paul Brennan (PB) joined MK to travel to UNAM to deliver the training. Support was also received from Nelago Indongo (NI) of UNAM and Daniel Farewll (DF) and Chao Huang (CH) of Cardiff University.
	
##Results

The course ran for three days from 12-14th of June in the computing lab WXXXX in the science block. This room easily hosted the 20 delegates that signed up for the course. Delegates, their affiliations (where known) and contact details are supplied in Appendix 1. 
The timetable of the event is provided in table 1. 


learnR timetable||
-----|------|-----
Day 1 ||
 Time |	Session|	Lead
09.00 – 09.30|	Installation |	All
09.30 – 10.00|	Ice-breaker	|MK
10:00 – 11:00|	Introduction to R|	MK
11:00 – 11.30|	Coffee	|
11.30 – 12.30|	Getting data into R|	MK
12.30 – 13.30|	Lunch	|
13.30 – 14.30|	Dataframes	|DG
14.30 – 15:00|	Coffee	|
15:00 – 16.00|	Manipulating data|	MK
16:00 – 16:30|	Questions & summary|	ALL
Day 2 | |
09.30 – 11.00|	Graphing/visualization and exploring data Part I	|PB
11:00 – 11.30|	Coffee	
11.30 – 12.30|	Graphing/visualization and exploring data Part II|	PB
12.30 – 13.30|	Lunch	|
13.30 – 14.30|	Linear models part I	|MK
14.30 – 15:00|	Coffee	|
15:00 – 16.00|	Linear models Part II|	MK
16:00 – 16:30|	Questions & summary	|ALL
Day 3 ||
09.30 – 11:00|	Generalised linear models|	MK
11:00 – 11.30|	Coffee	
11.30 – 12.30|	Delegate data sharing	|UNAM 
12.30 – 13.30|	Lunch	
13.30 – 14.30|	Reporting, scientific writing, interpretation|	DG
14.30 – 15:00|	Coffee	
15:00 – 16.00|	Markdown, trouble shooting, reusable workflows|	PB
16:00 – 16:30|	Questions/troubleshooting/summary	|MK


##Appendix 1
```{r eval=T}
delegates <- read.csv("/Users/Mark/Documents/GitHub/learnR/data/delegates.csv")
delegates[1:3]
```

